Live Functional Programming with Typed Holes

### 2018-04-15 calculus.tex
fewer words

The supplemental material includes our Agda-based
mechanization  \cite{norell2009dependently,norell:thesis} 
of the semantics and metatheory of \HazelnutLive, 
including proofs of all of the theorems stated above and all necessary lemmas\todo{make this so ian!}{}. 
%
%We choose the 
%(as did the mechanization of \Hazelnut by \citet{popl-paper}, though only a few definitions are common). 
%
%Agda is a good choice because it is designed to explicitly communicate a proof's structure, as is our goal, rather than relying on proof automation. 
%
A%gda itself was also an inspiration for this work because it supports holes, albeit in a more limited form than described here (cf. Sec.~\ref{sec:intro}). 
%
The basic approach is standard: we model judgements as 
inductive datatypes, and rules as dependently typed constructors of these judgements\todo{cite something?}{}. 
%
We adopt Barendregt's convention for bound variables \cite{urban,barendregt84:_lambda_calculus} and encode typing 
contexts, hole contexts and hole environments using metafunctions.\todo{say something about axioms?}{}

>>>>

The supplemental material includes our Agda-based
mechanization  \cite{norell2009dependently,norell:thesis} 
of the semantics and metatheory of \HazelnutLive, 
%including proofs of all of the 
for the theorems stated above, and all necessary lemmas\todo{make this so ian!}{}. 
%
%We choose the 
%(as did the mechanization of \Hazelnut by \citet{popl-paper}, though only a few definitions are common). 
%
%Agda is a good choice because it is designed to explicitly communicate a proof's structure, as is our goal, rather than relying on proof automation. 
%
%Agda itself was also an inspiration for this work because it supports holes, albeit in a more limited form than described here (cf. Sec.~\ref{sec:intro}). 
%
%
Our approach is standard: We model judgements as 
inductive datatypes, and rules as dependently typed constructors of these judgements\todo{cite something?}{}. 
%
We adopt Barendregt's convention for bound variables \cite{urban,barendregt84:_lambda_calculus} and encode typing 
contexts, hole contexts and hole environments using metafunctions.\todo{say something about axioms?}{}
